Computing properties of independent sets by generic programming tensor networks \thanks{\funding{...}}

### 2022-01-08 paper/paper.tex
finish intro

In this paper, we focus on independent set \textit{property} computation. % We introduce a generic programming tensor-network framework to compute the various \textit{properties} pertaining to independent sets. 

@@

We map the computation of these independent set properties into generic tensor network contraction with specially designed tensor element algebra. This is different from standard tensor network methods, where tensor elements are restricted to standard number types such as floating point numbers and integers.

@@

The complexity of our tensor-network based algorithms is similar to that of dynamic programming algorithms~\cite{Courcelle1990, Fomin2013} that dedicated to solving MIS size,

@@

This indicates it is a method that works better for sparse graphs or graphs,

@@

We benchmark our algorithms by computing various independent set properties of certain sparse graphs on central processing units (CPUs) and graphics processing units (GPUs); the high performance of our algorithms benefits from recent advances in random tensor-network contraction for the purposes of quantum circuit simulations~\cite{Gray2021, Pan2021, Kalachev2021}.
Algorithms have been developed to optimize the contraction order for tensor networks up to thousands of vertices, which produces a near-optimal space complexity of $2^{\sim{\rm tw}(G)}$ for contracting the tensor network.

>>>>

In this paper, we focus on computing various independent set \textit{properties}. % We introduce a generic programming tensor-network framework to compute the various \textit{properties} pertaining to independent sets. 

@@

We map the computation of these independent set properties into generic tensor network contraction with specially designed tensor element algebra.
It is different from the standard tensor network methods in that the tensor elements are not restricted to standard number types such as floating point numbers and integers.

@@

The complexity of our tensor-network based algorithms is similar to that of dynamic programming algorithms~\cite{Courcelle1990, Fomin2013} that dedicated to solving the MIS size,

@@

This indicates it is a method that works better for sparse graphs,

@@

We benchmark our algorithms by computing various independent set properties of certain sparse graphs on central processing units (CPUs) and graphics processing units (GPUs) and show its good performacne.
The high performance of our algorithms benefits from recent advances in random tensor-network contraction for the purposes of quantum circuit simulations~\cite{Gray2021, Pan2021, Kalachev2021},
where efficient heuristic algorithms have been developed to optimize the contraction order for tensor networks up to thousands of vertices.
